QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-19 Response/Paper_Res.tex
Rev_V6.3

\textcolor{blue}{In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}

%In this respect, we model the problem by introducing queuing theory in a dynamic MEC environment, so that our work will be closer to real conditions and easier to apply in practice.

%In contrast to the aforementioned works [9]–[20], we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands. We also explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, posing a more intricate challenge.

%While DRL-based methods DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. Current research primarily focuses on minimizing energy consumption, reducing processing delays, maximizing computation rates, or optimizing a weighted balance among performance factors. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, but also by energy consumption. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. While some existing works have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly.

% In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands. %We also explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, posing a more intricate challenge.

%First, prior research in \cite{yang2018distributed} - \cite{shah2018hierarchical} - \cite{9253665} considered delay-tolerant tasks, which may not be realistic due to the real-time processing demand by high computational tasks. Compared to these works, we explore a different and more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, which presents a more challenging problem. The impact of processing deadlines on the dynamic workload at the edge nodes influences the delay experienced by the offloaded tasks. 
% Albeit some existing works such as \cite{gong2022edge},  \cite{wu2024combining},  \cite{liao2023online},  \cite{wu2024privacy}, \cite{dai2020edge}, \cite{gao2022large}

%The works \cite{jovsilo2019wireless}-\cite{yang2018distributed} considered delay-tolerant tasks, which may have a limited applicability due to the real-time processing demand of high computational tasks. Compared to these works, we explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, which poses a more complex challenge.

%Nevertheless, prior research in \cite{huang2019deep}-\cite{gao2022large} fails to tackle some or all of these challenges.

%Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. First, some existing works such as [] - [] considered delay-tolerant tasks, which may not be realistic due to the real-time processing demand by high computational tasks. Compared to the aforementioned works [10]–[15], we explore a different and more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, which presents a challenging problem. The impact of processing deadlines on the dynamic workload at the edge nodes influences the delay experienced by the offloaded tasks. Second, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay as assumed in \cite{zhao2019deep}-\cite{9253665}, but also by energy consumption. Nevertheless, prior research in \cite{huang2019deep}-\cite{gao2022large} fails to tackle some or all of these challenges. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. In contrast to these works [18]–[21], we aim to propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands, inferred from their state.

%Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. First, Some existing works such as [] - [] considered delay-tolerant tasks, which may not be realistic due to the real-time processing demand by high computational tasks. Comparing with the aforementioned works [10]–[15], we consider a different and more realistic MEC scenario.  We take into account delay-sensitive tasks with processing deadlines, which is chalenging to address because the processing deadlines will affect the load level dynamics at the edge nodes and hence affect the delay of the offloaded tasks. Secound, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay as assumed in  \cite{zhao2019deep}-\cite{9253665}, but also by energy consumption. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. Nevertheless, prior research in \cite{huang2019deep}-\cite{gao2022large} fail to tackle some or all of these challenges. Different from those works [18]–[21], we aim to propose a DRL-based distributed algorithm that provide users with stricking balance among QoE factors based on their demands, caming from their state in each time.

%In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm, which empowers MDs to make offloading decisions and selecting appropriot EN utilizing only locally observed information, such as task size, queue details, energy status, and historical workloads at the ENs. Speaceficlly, by estimating the EN's dynamic workload, QECO efficiently handle task offloading in uncertain MEC environment, lead to improving overal system performance. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

%Inspired by existing studies, we delve into the challenge of computation task offloading in MEC systems, where the presence of strict task processing deadlines and energy constraints can adversely affect system performance and cause task delays. We proposes a decentralized offloading algorithm that empowers MDs to make intelligent decisions about offloading. The primary focus of our research is on the partial STO problem, where tasks can be fragmented into smaller sub-tasks, and the workloads at ENs can fluctuate dynamically and unpredictably. Our primary objective is to enhance the users' QoE individually. To define the problem, we have formulated the energy constraint MEC system as a Markov decision process (MDP) problem. To solve the MDP problems, Reinforcement Learning provides a range of solution methods such as dynamic programming, Monte Carlo methods, and temporal-difference learning. To deal with the Curse of Dimensions, modern Reinforcement Learning methods apply nonlinear function approximation, such as deep Q-network (DQN), to solve the problem with large state and action spaces. In our proposed approach, we leverage deep Q-learning \cite{mnih2015human}, a model-free DRL technique that enables agents to make informed decisions based on local observations without explicit knowledge of the system's dynamics and modeling. Compared to other researches, our approach provides a more realistic MEC scenario and a promising solution to the challenging problem of task offloading with strict deadline constraints. The proposed algorithm, by only utilizing locally observed information, allows each MD to determine the offloading decision in a decentralized manner.

@@

	\item \textit{DRL-based Offloading Algorithm:} \textcolor{blue}{To solve the problem of long-term QoE maximization in highly dynamic mobile environment, we propose QECO algorithm based on DRL that empowers each MD to make offloading decisions independently, without prior knowledge of the other MDs' tasks and offloading models. 		
		With a focus on the MD's QoE preference, our approach leverages dueling double deep Q-network (D3QN) \cite{wang2016dueling} to prioritize and strike an appropriate balance between QoE factors. 
		To handle the uncertainty of workloads at ENs, we integrate long short-term memory (LSTM) \cite{hochreiter1997long} into D3QN, enabling MDs to forecast ENs' workloads over time and improve the estimation of long-term QoE. Additionally, we provide an analysis of the training convergence and computational complexity of the proposed algorithm.}

@@

@@

\underline{Authors' Reply}: To address the reviewer’s comment, we have further explained how the proposed algorithm enhances the performance of the computation offloading in MEC and specified the contributions. We have also highlighted the role of the LSTM network and its impact on the convergence and performance of the QECO algorithm. First, to further clarify our contributions, we have revised Section I as follows.

@@

			\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.} \vspace{2mm}

@@

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). Given task completion, task delay, and energy consumption as the QoE requirements of mobile devices (MDs), this approach concentrates on maximizing the long-term QoE, by effectively utilizing the resources and properly handling the dynamic nature of workload at ENs. \vspace{2mm}

\end{itemize}
\dots
}}
\end{my}
\vspace{5mm}

@@

	\underline{Authors' Reply}: To address the reviewer's comments, we have further explained the QoE function and revised Section III as follows.

@@

@@

@@

				\,\,\,\,Some studies explored task offloading problems in more advanced scenarios. \dots 
				To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent deep Q-network (DQN)-based algorithm.

@@

				\,\,\,\,To reflecting real-world scenarios more accurately \dots 
				To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.

@@

				\,\,\,\,Due to the limited processing capacities of ENs  \dots
				To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.

>>>>

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
\textcolor{blue}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into the D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust their offloading strategies to improve long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

	\item \textit{DRL-based Offloading Algorithm:} \textcolor{blue}{To solve the problem of long-term QoE maximization in highly dynamic mobile environments, we propose the QECO algorithm based on DRL, which empowers each MD to make offloading decisions independently, without prior knowledge of other MDs' tasks and offloading models. Focusing on the MD's QoE preference, our approach leverages D3QN and LSTM to prioritize and strike an appropriate balance between QoE factors while accounting for workload uncertainty at the ENs. QECO empowers MDs to anticipate the EN's load level over time, leading to more accurate offloading strategies. We also analyze the training convergence and computational complexity of the proposed algorithm.}

@@

%\textcolor{blue}{\,\,\,\,To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
%	While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
%	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.} \vspace{2mm}

@@

\underline{Authors' Reply}: The proposed approach is designed to balance and prioritize QoE factors based on individual mobile device requirements while considering the dynamic workloads of edge nodes (EN). The QECO algorithm captures the dynamics of the MEC environment by integrating the Dueling Double Deep Q-Network (D3QN) model with Long Short-Term Memory (LSTM) networks. These algorithms address the QoE maximization problem by efficiently utilizing resources from both mobile devices and edge servers.

\begin{itemize}

	\item D3QN: By integrating both Double Q-learning and Dueling Network Architectures, D3QN overcomes overestimation bias in action-value predictions and accurately identifies the relative importance of states and actions. This significantly improves the model's ability to make accurate predictions, providing a foundation for enhanced offloading strategies.\vspace{2mm}

	\item LSTM: The incorporation of LSTM networks allows the model to continuously estimate dynamic workloads at edge servers. This feature is crucial for dealing with limited global information and adapting to an uncertain environment. By predicting the future workload of edge servers, mobile devices can effectively adjust their offloading strategies to achieve higher QoE.\vspace{2mm}

%This approach results in more accurate and context-aware offloading strategies that improve QoE for end-users.\vspace{2mm}

To address the reviewer’s comment, we have further explained how the proposed algorithm enhances the performance of the computation offloading in MEC and specified the contributions. We have also highlighted the role of the LSTM network and its impact on the convergence and performance of the QECO algorithm. First, to further clarify our contributions, we have revised Section I as follows.

@@

			\color{black}

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
\textcolor{blue}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into the D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust their offloading strategies to improve long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

	\item \textit{DRL-based Offloading Algorithm:} \textcolor{blue}{To solve the problem of long-term QoE maximization in highly dynamic mobile environments, we propose the QECO algorithm based on DRL, which empowers each MD to make offloading decisions independently, without prior knowledge of other MDs' tasks and offloading models. Focusing on the MD's QoE preference, our approach leverages D3QN and LSTM to prioritize and strike an appropriate balance between QoE factors while accounting for workload uncertainty at the ENs. QECO empowers MDs to anticipate the EN's load level over time, leading to more accurate offloading strategies. We also analyze the training convergence and computational complexity of the proposed algorithm.}

\dots
}}
\end{my}
\vspace{5mm}

@@

	\underline{Authors' Reply}: Given the importance of evaluating an agent's actions in DRL-based computation offloading approaches, we define the QoE maximization problem by considering several key performance factors. QoE is a time-varying performance measure that reflects user satisfaction and is influenced by more than just delay or energy consumption. On the other hand, investigating the trade-off between delay and energy consumption alone may not adequately address user demands or meet QoE requirements. To capture the agent’s personalized QoE needs, we designed an adaptive trade-off between task completion and cost reduction. In this model, the associated cost is a weighted sum of completion delay and energy consumption, with the weights dynamically adjusting based on the MD's preferences.\vspace{2mm}

	To address the reviewer's comments, we have further explained the QoE function and revised Section III as follows.

@@

	\begin{my}{1cm}{1cm}
		\rev{
			{
				\color{black}

@@

				\,\,\,\,To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
				\dots
					\textcolor{blue}{Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay.}

@@

				\,\,\,\,Some studies explored task offloading problems in more advanced scenarios. \dots 
					\textcolor{blue}{To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent deep Q-network (DQN)-based algorithm.}

@@

				\,\,\,\,To reflecting real-world scenarios more accurately \dots 
					\textcolor{blue}{To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.}

@@

				\,\,\,\,Due to the limited processing capacities of ENs  \dots
					\textcolor{blue}{To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.}

### 2024-10-19 Revision/Paper_Rev.tex
Rev_V6.3

 \textcolor{blue}{To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.}

@@

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
  \textcolor{blue}{To capture the dynamic nature of the MEC environment, we leverage the dueling double deep Q-network (D3QN) to strike a balance among QoE factors based on user preferences. Specifically, D3QN improves upon standard DQNs by incorporating both double Q-network and dueling architectures, which reduce overestimation bias in action values and better distinguish the significance of states and actions. Moreover, to effectively handle the uncertainty of the MEC environment where global information is unavailable, we integrate long short-term memory (LSTM) into the D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to proactively adjust their offloading strategies and improve the estimation of long-term QoE.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

@@

\section{Related Work}
\label{section:II}
%\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT), Internet of Vehicles (IoV), and Industrial IoT (IIoT)  environment.

%Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, 
%Internet of Vehicles (IoV) \cite{Bolourian-WCL24}, 
%and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}

%, while uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges in MEC systems with limited resources.

 \textcolor{blue}{In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.}

 \textcolor{blue}{\subsection{DRL-based Computation Offloading for MEC}
To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. 
Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios.}

@@

In this paper, we focused on addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. We formulated an optimization problem that aims to maximize the QoE of each MD individually, while QoE reflects the energy consumption and task completion delay. To address the dynamic and uncertain mobile environment, we proposed a QoE-oriented DRL-based computation offloading algorithm called QECO. Our proposed algorithm empowers MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QECO algorithm not only adapts to the uncertain dynamics of load levels at ENs, but also effectively manages the ever-changing system environment. Through extensive simulations, we showed that QECO outperforms several established benchmark techniques, while demonstrating a rapid training convergence. Specifically, QECO increases the average user's QoE by 37\% compared to an existing work. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, under different system conditions and varying user demands.

>>>>

@@

@@

To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
  \textcolor{blue}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into the D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust their offloading strategies to improve long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

\section{Related Work}
\label{section:II}
%\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT), Internet of Vehicles (IoV), and Industrial IoT (IIoT)  environment. 
%Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, 
%Internet of Vehicles (IoV) \cite{Bolourian-WCL24}, 
%and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}
%, while uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges in MEC systems with limited resources. 
 \textcolor{blue}{In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.}
 \textcolor{blue}{\subsection{DRL-based Computation Offloading for MEC}
To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. 
Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios.}

@@

In this paper, we focused on addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. We formulated an optimization problem that aims to maximize the QoE of each MD individually, while QoE reflects the energy consumption and task completion delay. To address the dynamic and uncertain mobile environment, we proposed a QoE-oriented DRL-based computation offloading algorithm called QECO. Our proposed algorithm empowers MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QECO algorithm not only adapts to the uncertain dynamics of load levels at ENs, but also effectively manages the ever-changing system environment. Through extensive simulations, we showed that QECO outperforms several established benchmark techniques, while demonstrating a rapid training convergence. Specifically, QECO increases the average user's QoE by --\% compared to an existing work. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, under different system conditions and varying user demands.
